Global adjoint tomography -- Model GLAD-M25

### 2018-10-09 main.tex
add North America section

The post-processing takes the frechet derivatives as the input and generate
the model updates as the output. It contains:
\begin{enumerate}
  \item Summation of each kernel for each earthquake to obtain one
    gradient for the overall misfit function. The number of kernel
    files will reduce from 1480 to 1 after summing them up. Also,
    there will source weightings applied at this stage, to balance
    the uneven distribution of earthquakes.
  \item Smoothing the misfit gradient using 3D gaussian function, which
    serves as a regularization procedure. Instead of using a changing
    smooth radius based upon the "ray density"\citep{bozdaug2016global},
    we used the fixed value in the same iteration, following\cite{hu2012structure}.
  \item Precondition the smoothed kernels. Following
    \citep{luo2013strategies, zhu2012structure, bozdaug2016global},
    the preconditioner we used is:
    \begin{equation}
      P(\mathbf{x}) = 1 / \int \partial_t^2 \mathbf{s}(\mathbf{x}, t) \cdot \partial_t^2 \mathbf{s}^\dagger(\mathbf{x}, T-t) dt
    \end{equation}
\end{enumerate}

@@

\subsection{Depth cross-section}

\begin{figure}
\includegraphics[width=0.9\textwidth]{figures/depth_slice/globe_vs.pdf}
  \caption{Map views of global $V_s$ perturbations at various depths for out model GLAD-M25(left column), S362ANI+M(middle column)\citep{moulik2014anisotropic} and S40RTS(right column)\citep{ritsema2011s40rts}. The perturbations are calculated based on each model's own 1D profile. The values(upper-left corner of each figure) denotes the minimum/maximum perturbations for each model at the corresponding depth. The green circles denotes the locations of hotspots\citep{montelli2006catalogue}. The range of the colorbar is the same for each row and the range value is labeled on the most left, right after the depth.}
\label{fig:global-vs}
\centering
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.9\textwidth]{figures/depth_slice/globe_vp_LLNL-GAP.pdf}
  \caption{Map views of global $V_p$ variations at various depths for our model GLAD-M25(left column), S362ANI+M(middle column) and LLNL-G3Dv3(right column)\citep{simmons2012llnl}. For LLNL-G3Dv3, the depths is labeled on the right bottom based on its own mesh spacing. Other plotting conventions are used similar as in Figure \ref{fig:global-vs}.}
\label{fig:global-vp}
\centering
\end{figure}

@@

@@

@@

@@

@@

>>>>

The post-processing takes the frechet derivatives as the input and generate
the model updates as the output. It contains:
\begin{enumerate}
  \item Summation of each kernel for each earthquake to obtain one
    gradient for the overall misfit function. The number of kernel
    files will reduce from 1480 to 1 after summing them up. Also,
    there will source weightings applied at this stage, to balance
    the uneven distribution of earthquakes.
  \item Smoothing the misfit gradient using 3D gaussian function, which
    serves as a regularization procedure. Instead of using a changing
    smooth radius based upon the "ray density"\citep{bozdaug2016global},
    we used the fixed value in the same iteration, following\cite{zhu2012structure}.
  \item Precondition the smoothed kernels. Following
    \citep{luo2013strategies, zhu2012structure, bozdaug2016global},
    the preconditioner we used is:
    \begin{equation}
      P(\mathbf{x}) = 1 / \int \partial_t^2 \mathbf{s}(\mathbf{x}, t) \cdot \partial_t^2 \mathbf{s}^\dagger(\mathbf{x}, T-t) dt
    \end{equation}
\end{enumerate}

@@

\subsection{Global Velocity Structure}
In Fig.\ref{fig:global-vs}, the global map of isotropic $V_s$ is plotted at certain depths.
As comparisons, we also plotted two other models, S362ANI+M{\citep{moulik2014anisotropic},
which is the updated version of our starting model but with mode data added
into the inversion, and S40RTS\citep{ritsema2011s40rts}. At the first glance,
you may notice that all the models agree at the long wavelength structures.
At 2800km depth, our model is very close to S362ANI+M, with more extended
features at the LLSVP.

The value ranges are labeled on the top left on each figure. It is obvious the
value ranges in our model is generally larger than other two models, which is
consistent with \cite{french2014whole}.

\begin{figure}
  \centering
  \includegraphics[width=0.9\textwidth]{figures/depth_slice/globe_vs.pdf}
  \caption{Map views of global $V_s$ perturbations at various depths for out model
  GLAD-M25(left column), S362ANI+M(middle column)\citep{moulik2014anisotropic}
  and S40RTS(right column)\citep{ritsema2011s40rts}. The perturbations are
  calculated based on each model's own 1D profile. The values(upper-left corner
  of each figure) denotes the minimum/maximum perturbations for each model at
  the corresponding depth. The green circles denotes the locations of
  hotspots\citep{montelli2006catalogue}. The range of the colorbar is the same
  for each row and the range value is labeled on the most left, right after
  the depth.}
  \label{fig:global-vs}
\end{figure}

@@

The other prominent feature of our models is that we can also constrain $V_p$ as an
independent model parameters. Fig.\ref{fig:global-vp} shows our isotropic $V_p$
structures at serveal depths. As comparisons, we also showed two more global
$V_p$ models, LLNL-G3Dv3\citep{simmons2012llnl}} and GAP-P4\citep{fukao2013subducted}.

At 100km depth, our model shows prominent ocean ridges at the realm of pacific
oceans, which are relatively slow velocity regions, compared to other two vp models.
On the other hand, the continent slabs, such as Australia, South Africa,
North America and Europe, is more prominent in our model.

For upper mantle, the LLNL-G3Dv3 shows the largest variations. For example,
the 500km, the LLNL model shows very strong slow velocity anomalies at
Hawaii and other pacific hotspots, such as Samoa and Tahiti.
For middle mantle at about 1000km, all them models all shows a few major
subduction zones, such as the south america, Fiji and Sumatra regions.
At lower mantle, such as 2000km and 2800km, LLNL-G3Dv3 and GAP-P4 tends to
fade out, even though the patterns are very similar among them, such as
the LLSVP regions.

** Note: add sphereical hormonica analysis later **

\begin{figure}
\includegraphics[width=0.9\textwidth]{figures/depth_slice/globe_vp_LLNL-GAP.pdf}
  \caption{Map views of global $V_p$ variations at various depths for our model
  GLAD-M25(left column), LLNL-G3Dv3(middle column) \citep{simmons2012llnl} and
  GAP-P4(\citep{fukao2013subducted}).
  For LLNL-G3Dv3, the depths is labeled on the right
  bottom based on its own mesh spacing. Other plotting conventions are used
  similar as in Figure \ref{fig:global-vs}.}
\label{fig:global-vp}
\centering
\end{figure}

For the following sections, we will discuss the velocity structures in regional
areas.

\subsubsection{North America}
The deployment of USArray has dramatically incresed the data overage on the
continental United States. In this section, we compare our GLAD-M25 with
together with two global models, S362ANI+M, S40RTS, and two regional models,
US22\citep{zhu2017radial}, SL2013NA\citep{schaeffer2014imaging}.

US22 is radially anosotropic model build based on adjoint tomography using
USArray data from 180 regional earthquakes using 15-50sec short-period
body waves and 25-150sec long-period surface waves.
SL2013NA is an uppe-matnle global shear wave speed model using multimode
surface wavefrom tomography and primally focused on the north american
region.

The North American region is featured by a large, high-velocity cartonic
lithosphere, bounded by the Rocky Mountain Front to the west and continental
margein to the east. For both sides the lithosphere has been deformed by
low velocity structures thus form a sharp boundary.

At 100km, our model shows a much sharpened boundary between the carton
and surrounding low veclocity strcutures, especially compared with
two global models, S362ANI+M and S40RTS, yet stay very similar to
two regional models, US22 and SL2014NA. At such depth,
we are observed a very strong expression of the Snake River Plain(
with YellowStone) and Raton hotspot, with their depth extending to 200km.
The very high-velocity caraton extend to 200km, with its very core part to
300 km, similiar to US22 while SL2013NA shows it almost disappeared at such depth.
Again, the Wyonming craton and Mecicine Hat Block shows a very strong lithospheric
root from the very shallow depth to 400km, which is also smiliar to US22 but
hard to observe in SL2013NA. Similiar case is the craton at Yavapai and
Mazatzal Blocks, which define the souther bound of the large craton.

At such depth, we also observed high velocity
features within the Gulf of Mexico, which conincides spatially with the deepest
bathymetry and corresponds to a portion of anciet oceanic
Lithosphere\citep{muller2008}. The remanant of Juan de Fuca subudction
plates, with its high velocity footprint, is presented in our model at
300km and 400km, though the SL2013NA shows a much stronger anomaly.

At the North, our models shows a extended high veloicty craton beneath the 
Greenland, though clearly seperated with the North America Craton,
bounded at the relativly low velcoity strcture at Barffin Bay and Labrador
Sea, with North American Craton followed nicely with the coastline. In the
north west region, our models shows the most clear picture of
Aleutian subduction zones, with it high velocity feature down to 400km.
In the nort easter part, the Iceland hotspot has been greatly enhanced,
especially at 300km and 400km compared to S362ANI+M.

In the Easter part, our models shows a high-velocity structure at the western
Atlantic, starting from the tip of Florica to the New York,
seperated from the major part the north america craton,
though it stays very thin that the depth only extend to above 200km.
This feature is associated with some of the oldest oceanic crust and lithosphere
within the Atlantic\citep{muller2008, schaeffer2014imaging}.
All the models is showing a high velocity anomaly at Nova Scotia and Newfoundland
with its high-velocity core to 300km.
Bermuda hotspot is nicely perserved from our starting
model, yet get sharpened and stronger at 200km and 300km. Besides, the
Carribean suduction, which is relatively young subduction systems, is clearly
observable in our model, starting from 200km to 300km.

For even deeper depth, our models shows a very clear picture of the Farallon
subductions, but it goes beyond the range of this comparison since the two
region models are really upper-mantle models which don't extend to the very
deep depth. We will show some vertical cross-sections of Farallon slabs in
the later sections.

@@

\subsubsection{Europe}
Fig.\ref{fig:europe-vs} shows the isotropic $V_s$ structures at Europe. As
comparisons, we also showed S362ANI+M, S40RTS and one regional model EU60
\citep{zhu2015seismic}. Compared to two global models, it is clear that
our model is much sharper at few locations. At 100 and 200km, Eifel
hotspot is clearly seen in our models, as well as in EU60. At 400km
and 600km, the subduction is very consistent between GLAD-M25 and EU60,
with the curved shape at the lower bottom of the figure,
while S362ANI+M shows very smooth shape and S40RTS shows much smaller 
perturbation values. Besides, at 400km, GLAD-M25 is enhancing Iceland
compared to S362ANI+M.

@@

\subsubsection{Asia}

We presented our model GLAD-M25, with S362ANI+M, S40RTS and EARA2014.
At 100km depth, our model shows sharpening at the Himalayas subductions
zones. At 250km, our models shows the subudction in the east part.
At 400km, our models shows the subduction at sumartra.

@@

\subsubsection{South America}

@@

In this section, we will visit the plumes systems on the earth.

@@

In this sections, we will visit some of the well-known subduction zones.
